Summary of Changes in response to Referee's Report

### 2016-01-12 curves-write-up/AIF/changes-summary.tex
edited changes-summary adding in difference for hilbert polynomials

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
\end{enumerate}

\section{Other suggestions}
The referee also made the following suggestions.

\begin{enumerate}
	\item Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$ and
		we range over all integers $s_i$ instead of odd integers $e_i$.
\end{enumerate}

>>>>

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item We included Hilbert polynomial in Examples $3.2- 3.5$.
	\item We replaced ``best lower approximation'' with Hirzebruch--Jung
		fractions
\end{enumerate}

\section{Other suggestions}
The referee also made the following suggestions.
\todo{Aaron: Since there's only one thing here, can we remove this enumerate?
Alternatively, if we do end up including more than one of these, can we give the suggestion
and response together, instead of listing all the suggestions and then all the responses?}
\begin{enumerate}
	\item Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$ and
		we range over all integers $s_i$ instead of odd integers $e_i$.
\end{enumerate}
